Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-10-18 R0V0_ian.tex
Add / change files

\begin{figure}
	\centering
%	\includegraphics[]{}
	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
	\includegraphics[width=\columnwidth]{./imgs/physical_network_graphs}
	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
	\label{fig:graph different illustration}
\end{figure}

@@

\begin{definition}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t),\Delta(t))\leq -\lambda V(X(t),\Delta(t))
 	 	 \end{equation}
 	 	 holds, where $X(t):=X(t,x,u)$ and $\Delta(t):=\Delta(t,x,\delta_x,u,0)$, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

\begin{definition}[{\cite{Manchester2014a}}]
	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\to\mathbb{R}^{n\times m}$.

@@

\mypara Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them. Then the differential feedback law $K(x)$ can be integrated along $\gamma$:
\begin{equation}\label{eq:contracting feedback law}
	k(t)=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, each function $W_i$ depends only on the state of system $i$. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W-W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. Also, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}

@@

\section{Scalable Design of Distributed Controllers}\label{sec:distributed_design}

\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem to satisfy the set of equations~\eqref{eq:main result}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. Thus, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be scalable, in the sense that adding more agents to the network will make the time taken to compute the controller linearly. To that end chordal graphs are employed to decompose the network topology into smaller complete components.

\begin{proposition}\label{prop:clique tree decomposition}
	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $l$ matrix inequalities with smaller dimension. Furthermore, each of the matrix inequality correspond to a clique, and for each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in it, the matrix inequality depends on $x_i, \breve{x}_i$ and $\vec{x}_i$. Finally, whenever each matrix inequality holds uniformly over its argument, the set of Equations~\eqref{eq:MI:SSCCM} is satisfied.
\end{proposition}

\begin{proof}
	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$. Let the integer $l>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_l$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,l]}$. For each index $k\in\mathbb{N}_{[1,l]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

\mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$. The existence of $l$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,l]}$, satisfying the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k\;.
  	\end{equation*}

\mypara Without loss of generality, assume that the node $i\in\mathscr{V}_c$ is contained in the clique $\mathscr{C}_k$. Whenever the following matrix inequality 
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,l]},
	\end{equation}
	holds uniformly, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds.

	For each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in the clique $\mathscr{C}_k$. The corresponding matrix $F_k$ has arguments $x_i, \breve{x}_i$ and $\vec{x}_i$. In other words, $F_k$ depends on how strongly the nodes of the of the system (defined by $\mathscr{G}_c$) and communication network (defined by $\mathscr{G}_p$) are connected among each other. This concludes the proof.
\end{proof}

@@

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.

@@

\mypara The solver took 31 seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

@@

\mypara The time taken by solver to find a solution to the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&\overline{Y}_2(\cdot)&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&\overline{Y}_3(\cdot)&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$. The time taken by the solver to find a solution to the set of matrix inequalities~\eqref{eq:main result} was 2.5 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&31s\\
	Neighbor&3s\\
	Fully decentralized&2.5s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:chain case}
\end{table}

@@

\mypara The solver took 32s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
\begin{equation*}
	W=\mathbin{\mathtt{diag}}(0.1,1,0.1,1,0.1,1,0.1,1,0.1,1,0.3,1).
\end{equation*}
The matrix $Y$ is given by
\begin{equation*}
	\begin{bmatrix}
		\overline{Y}_{11}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&\underline{Y}_{22}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&\overline{Y}_{33}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{44}(q)&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{55}(q)&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\underline{Y}_{66}(q)
	\end{bmatrix},
\end{equation*}
for every $q\in\mathbb{R}^{12}$, where 
\begin{align*}
 \overline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&4+4\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},\\
 \underline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&2+2\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},
\end{align*}
for each index $i,j\in\mathbb{N}_{[1,6]}$.

\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network. More precisely, $\mathscr{G}_c=\mathscr{G}_p$. The solver took 17s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$. The solver took 12s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&32s\\
	Neighbor&17s\\
	Fully decentralized&12s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:mixed example}
\end{table}

>>>>

\begin{figure}
	\centering
%	\includegraphics[]{}
	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
	\includegraphics[width=\columnwidth]{./imgs/physical_network_graphs}

	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
	\label{fig:graph different illustration}
\end{figure}

@@

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t),\Delta(t))\leq -\lambda V(X(t),\Delta(t))
 	 	 \end{equation}
 	 	 holds, where $X(t):=X(t,x,u)$ and $\Delta(t):=\Delta(t,x,\delta_x,u,0)$, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\to\mathbb{R}^{n\times m}$.

@@

\mypara Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them. Then the differential feedback law $K(x)$ can be integrated along $\gamma$:
\begin{equation}\label{eq:contracting feedback law}
	k(x,=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W-W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}

@@

\section{Distributed Design of Distributed Controllers}\label{sec:distributed_design}

\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem to satisfy the set of equations~\eqref{eq:main result}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. In particular, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be done in parallel. To that end chordal graphs are employed. It utilizes the network topology to decompose it into smaller complete components.

\begin{proposition}\label{prop:clique tree decomposition}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension. Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI:SSCCM} is satisfied.
\end{proposition}

\begin{proof}
	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$. Let the integer $p>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

\mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$. The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k\;.
  	\end{equation*}

\mypara Consequently, whenever the following matrix inequality holds 
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]},
	\end{equation}
	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds. This concludes the proof.
\end{proof}

@@

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive. Further conditions are discussed in \cite{manchester_existence_2018}.

@@

\mypara The solver took 98  seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

@@

\mypara The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&\overline{Y}_2(\cdot)&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&\overline{Y}_3(\cdot)&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$. The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 4.4 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&98s\\
	Neighbor&3.5s\\
	Fully decentralized&4.4s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:chain case}
\end{table}

@@

\mypara The solver took 48s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
\begin{equation*}
	W=\mathbin{\mathtt{diag}}(0.1,1,0.1,1,0.1,1,0.1,1,0.1,1,0.3,1).
\end{equation*}
The matrix $Y$ is given by
\begin{equation*}
	\begin{bmatrix}
		\overline{Y}_{11}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&\underline{Y}_{22}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&\overline{Y}_{33}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{44}(q)&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{55}(q)&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\underline{Y}_{66}(q)
	\end{bmatrix},
\end{equation*}
for every $q\in\mathbb{R}^{12}$, where 
\begin{align*}
 \overline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&4+4\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},\\
 \underline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&2+2\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},
\end{align*}
for each index $i,j\in\mathbb{N}_{[1,6]}$.

\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network. More precisely, $\mathscr{G}_c=\mathscr{G}_p$. The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$. The solver took 43s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&48s\\
	Neighbor&57s\\
	Fully decentralized&43s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:mixed example}
\end{table}
